---
title: "rmss_models_for_paper *using latest exposures*"
author: "Daniel Dean"
date: "2024-11-21"
output: html_document
---

```{r setup, include=FALSE, root.dir = "..}
knitr::opts_chunk$set(echo = TRUE)

setwd("..") # probably a better way, but setting to be in main directory for more intuitive file paths
```
# Adding in steps from previous scripts; might tkae onger to run, but clearer as far as reviewing steps, keeping versions straight, etc.

# 1) Reading in RMSS data

```{r 01_population_read_in}

# reading in population data


## Loading packages

library(tidyverse)
library(ggplot2) # plotting pacakge
library(viridis) # package with new color ~schemes for ggplot;
# intended to be more color-blind accesible and to work with greyscale printing

###############
# loading a package to read excel files
#install.packages("openxlsx") # (comment out once installed so it doesn't run)
library(openxlsx)


setwd("/home/dad1717/Documents/erhs_postdoc_work/rms_study/")
  # hopefully consistent throughout! 


#######################
# skipping 1st row with notes to keep consistent cell formats
# Excel dates aren't read correctly by default, but fortunately there's an option to detect them
  
  # maybe set up as a function/file list 

rmss_data_21 <- read.xlsx(xlsxFile =  "01_raw_data/2.2021 to 12.31.2021 Leachman Ejacs.xlsx",
                          startRow = 2,
                          detectDates = TRUE)
rmss_data_22 <- read.xlsx(xlsxFile =  "01_raw_data/1.1.2022 to 12.31.2022 Leachman Ejacs.xlsx",
                          startRow = 2,
                          detectDates = TRUE)
rmss_data_23 <- read.xlsx(xlsxFile =  "01_raw_data/1.1.2023 to 10.20.23 Leachman Ejacs.xlsx",
                          startRow = 2,
                          detectDates = TRUE)

# same column names/types, so can easily merge the objects 
rmss_data <- rbind(rmss_data_21, rmss_data_22, rmss_data_23) 

rm(rmss_data_21, rmss_data_22, rmss_data_23) 

# I guess could make sense to hold on to an unfiltered version?
save(rmss_data, file = "01_5_processed_data/rmss_data.RData")

# filtering to bulls with >= 90 contiguous days of sampling
  # Oh, also remembering that we're filtering out ~rare statuses, so could do that here
  # warning about a -Inf result; looks like a single-reading bull, so while suboptimal,
    # makes sense that the time interval-based code wouldn't work

# count after removing group IDs: (shouldn't go towards 'raw' population)
rmss_data %>%
  group_by(Bull.Code) %>%
  filter(!str_detect(Bull.Code, "20\\d{2}")) %>%
  dplyr::select(Bull.Code) %>% unique() %>% nrow()

# OK, coming back and applying (hopefully) conservative filtering upstream

rmss_data_filtered <- rmss_data %>%
  group_by(Bull.Code) %>%
  filter(!str_detect(Bull.Code, "20\\d{2}")) %>%
  filter(Sts %in% c("Disc", "Pend")) %>% # includes only values matching a list
  mutate(pending = (Sts == "Pend")) %>%
  filter((sum(as.numeric(pending))/n()) > 0) %>% 
  mutate(Date_lead = lead(Date, 1)) %>%
  #dplyr::select(Date, Date_lead) %>%
  mutate(Date_diff = as.numeric(Date_lead - Date),
         test = purrr::accumulate(Date_diff, ~ifelse(.x < 90, .x + .y, 0),
                           .dir = 'forward'),
         test_filter = max(test, na.rm = T)) %>%
  filter(test_filter >= 90) %>%
  #mutate(simple_diff = sum(Date_diff, na.rm = T)) %>% 
  dplyr::select(-c(test, test_filter))
  # warning generated by apparently all-missing data?

save(rmss_data_filtered, file = "01_5_processed_data/rmss_data_filtered.RData")

# OK, let's keep separate just for clarity and ability to separate

rmss_data_filtered_no_coding <- rmss_data_filtered

rmss_data_filtered_coded <- rmss_data_filtered |>
  ungroup() |>
  dplyr::mutate(sample_id = row_number()) |>
  
  dplyr::mutate(Comment = tolower(Comment)) |>
  dplyr::mutate(behavior = str_detect(Comment, pattern = "mnt|mount|jmp|jump|interest|int|ej|thrust|fell|slid|sore|missed|ground|attempt|air|spook|spk|extension|spas|hit|extend"),
                implaus = str_detect(Comment, pattern = "tube|crack|seal|dirt|machine|dropped|spilled|manure"),
                bull_other = str_detect(Comment, pattern =  "blood|bld|bleed|urine|lam|trauma|footrot|urine|blood|bld|wart|abrasion|abbrasion"),
                gross_morph  = str_detect(Comment, pattern = "thick|thk|thin|thn|green|clr|semi")) |>
  dplyr::mutate(
    behavior = replace_na(behavior, FALSE),
    implaus = replace_na(implaus, FALSE),
    bull_other = replace_na(bull_other, FALSE),
    gross_morph = replace_na(gross_morph, FALSE)
  ) 

rmss_data_filtered <- rmss_data_filtered_coded |>
  dplyr::filter(implaus == FALSE)

save(rmss_data_filtered, file = "01_5_processed_data/rmss_data_filtered_CODED.RData")


# 11217 samples now...

# 61 days?

rmss_data_filtered_61d <- rmss_data %>%
  group_by(Bull.Code) %>%
  filter(Sts %in% c("Disc", "Pend")) %>% # includes only values matching a list
  mutate(pending = (Sts == "Pend")) %>%
  filter((sum(as.numeric(pending))/n()) > 0) %>% 
  mutate(Date_lead = lead(Date, 1)) %>%
  #dplyr::select(Date, Date_lead) %>%
  mutate(Date_diff = as.numeric(Date_lead - Date),
         test = purrr::accumulate(Date_diff, ~ifelse(.x < 61, .x + .y, 0),
                                  .dir = 'forward'),
         test_filter = max(test, na.rm = T)) %>%
  filter(test_filter >= 61) %>%
  #mutate(simple_diff = sum(Date_diff, na.rm = T)) %>% 
  dplyr::select(-c(test, test_filter))

save(rmss_data_filtered_61d, file = "01_5_processed_data/rmss_data_filtered_61d.RData")


################ Environmental Data? #########################
  # or as a separate script?

# Do I want to read in environmental data as well?
  # I guess feels a bit ~placeholder-like in terms of replicability

# could also use 
# rm(list = c('rmss_data_21', 'rmss_data_22') )
# removing old objects; kind of overkill, but good practice in general to keep resource use low

## Reading in PM data
# in this case, have to ~clip around PM data
pm_2_5_22 <- read.xlsx(xlsxFile = "01_raw_data/PM Data.xlsx",
                       detectDates = TRUE,
)

# signing up for API using https://aqs.epa.gov/data/api/signup?email=dad11493@colostate.edu
# from https://aqs.epa.gov/aqsweb/documents/data_api.html#signup


##################

# filtering/processing data

# checking sampling count by bull

rmss_data$Bull.Code %>% table()

# quick visualization of samples over time

# The '%>% (pipe?) operator is a ~building block forthe `tidyverse` workflow; e.g.
# data.frame %>% summary() is equivalent to 
# summary(data.frame)

# but as you can see below, it can get a bit more involved with piping `rmss data` into 
# mutliple downstream steps

# ggplot2 is a graphing ~ecosystem made by the same ~author (Hadley Wickham), but is I tink older and uses `+` in
# a similar capacity 

# detail including length of time and a binary classification where there are more/less than 91 days
# could reframe to months exactly if that were more relevant, but using default unit

rmss_filter_plot <- rmss_data %>% 
  group_by(Bull.Code) %>% 
  mutate(date_range = max(Date) - min(Date)) %>% 
  ggplot() +
  aes(y = Bull.Code,
      x = Date, 
      fill= date_range,
      color = date_range > 91) + # approx. 3 months
  geom_tile() + theme_minimal() + 
  scale_fill_viridis_c()
# a bit crowded, but hopefully gets the idea across

rmss_filter_plot # printing to plot viewer

rmss_data_filtered %>%  filter(!str_detect(Bull.Code, "20\\d{2}"), Sts %in% c("Disc", "Pend")) %>%
    group_by(Bull.Code) %>% mutate(`Breed Group` = as.factor(case_when(str_detect(Bull.Code, "A") ~ "British", !str_detect(Bull.Code, "A") ~ "Continental"))) %>%
    mutate(date_range = max(Date) - min(Date)) %>% 
    ggplot() + geom_rect(aes(xmin = min(Date), xmax = max(Date), ymin = Bull.Code, ymax = Bull.Code, color = `Breed Group`)) +
    geom_tile(aes(y = Bull.Code,
        x = Date, 
        fill= Sts)) +
    theme_minimal() + 
    scale_fill_manual(values = c("red4", "cyan3")) + labs(x = "Date", y = "Bull (identifier)", fill = "Status", title = "Samples by Collection Date, Bull ID, and Status") +scale_color_manual(values = c("azure3", "bisque"))

# can see sample frequency picks up in 2022

# can save plot images using buttons on the R Studio user interface, or using code like this:

ggsave(plot = rmss_filter_plot, 
       filename = "03_output/rmss_filter_plot_incl_2023_CODED.png", 
       height = 6,
       width = 7, bg = 'white')




# `group_by` followed by `mutate` is a bit involved;
# `mutate` creates a new column (which can also overwrite an original)
# by performing a user-defined operation on it (this could be as simple as e.g.
# `new_column = old_column` to create a duplicate, or could e.g. add two columns together)

# by default, `mutate` is applied over the entire dataframe, so we'd get a single column
# with the entire ~2-year range with just the `mutate` step above

# `group_by` lets us tell it to perform the `mutate` function within groups defined
# by some factor (or factor-coercible variable--in this case it's converting it from a character object type)

# `group_by` can also accept multiple columns to get groups considering multiple factors



# on the assumption this is correct, filtering could look like:

# using `dplyr` (part of the `tidyverse` set of functions; modeled more after 
# SQL, which is used for database queries, than base R, which is closer to Python
# and would use nested operations or custom multistep functions in the same place)

#rmss_data_filtered <- rmss_data %>%
#  filter(!str_detect(Bull.Code, "20\\d{2}")) %>%
#  group_by(Bull.Code) %>% 
#  mutate(date_range = (max(Date) - min(Date))) %>%  
#  filter(date_range > 91)

# checking # of bulls removed;

rmss_data$Bull.Code %>% unique() %>% length() # 153 initially
rmss_data_filtered$Bull.Code %>% unique() %>% length() # 82 with samples over at least 91 days 

# so removed 71 bulls, or ~46.4% of initial 'population'
# honestly more than I expected from the  visual 

# rmss_filtered now only includes bulls with data collected over >91 days

# plotting with the filtered dataset:

rmss_data_filtered %>% 
  group_by(Bull.Code) %>% 
  mutate(date_range = max(Date) - min(Date)) %>% 
  ggplot() +
  aes(y = Bull.Code,
      x = Date, 
      fill= date_range) + #,
  #color = date_range > 91) + # approx. 3 months; all should match now
  geom_tile() +
  theme_minimal() +  # setting a plot theme from a pregenerated templates
  scale_fill_viridis_c() # using a package-defined 

# by default, ggsave uses the last-rendered plot, which can be handy but probably isn't a best practice
ggsave(filename = "03_output/rmss_filter_plot_filtered_incl_2023.png", 
       height = 6,
       width = 7)



########## 
# looking a bit at rejected vs pending samples

rmss_data_filtered$Sts %>% table()
# oh, a handful of results other than Disc, Pend; do we want to keep these?
# `Fresh` (1), `NChg` (13)m `NoGo` (4)

# 4054/(10298+4054), so ~28% rejected including 2023 data

# 1589 Discarded vs 6007 pending, so ~20.9% rejection rate
  # so substantially higher rejection rate in 2023 data? (up almost 8 points)


# quick general visualization
rmss_data_filtered %>% 
  group_by(Bull.Code) %>% 
  mutate(date_range = max(Date) - min(Date)) %>% 
  ggplot() +
  aes(y = Bull.Code,
      x = Date, 
      fill= Sts) +
  geom_tile() + 
  theme_minimal() + 
  scale_fill_viridis_d() # moved to `_d` for discrete values 

rmss_data_filtered %>%  filter(!str_detect(Bull.Code, "20\\d{2}"), Sts %in% c("Disc", "Pend")) %>%
    group_by(Bull.Code) %>% 
    mutate(date_range = max(Date) - min(Date)) %>% 
    ggplot() +
    aes(y = Bull.Code,
        x = Date, 
        fill= Sts) +
    geom_tile() + 
    theme_minimal() + 
    scale_fill_manual(values = c("red4", "cyan3")) + labs(x = "Date", y = "Bull (identifier)", fill = "Status", title = "Samples by Collection Date, Bull ID, and Status")

# can see that some bulls are 100% accepted/rejected, while others have a mix of outcomes
# see some maybe-suspicious 'blocks' w/ same outcomes and dates--is it possible there might be duplicate IDs?


# looking at % accepted/rejected by bull:
# removing the other 3 outcomes for now...

rmss_data_filtered %>%
  filter(Sts %in% c("Disc", "Pend")) %>% # includes only values matching a list
  mutate(pending = (Sts == "Pend")) %>% # could just convert `Sts` to a True/False format, but wanted to make it clearer what's happening
  group_by(Bull.Code) %>% # grouping by bull again
  mutate(pending_pct = sum(pending)/length(pending)) %>% # simple ratio, but lots of ways to get this value
  dplyr::select(Bull.Code, pending_pct) %>%
  summary() # generates a 6-value summary of the results

# ranges from 0% -100% `pending' samples, with a fairly high mean/median of around 80% 
# 1st quartile is already 67.7%, so most bulls are accepted more often than not
# <-- interestingly per-bull ~average matches total population % pretty closely, although probably coincidental

# with 2023 data, 71-75% accepted (mean vs median), so again a slightly lower aceptance rate




```


# 2) AQS/etc. (environmental in general) read-in
  -think there are some extraneous steps here
  
```{r 01_exposure_read_in}


#install.packages(pkgs="RAQSAPI", dependencies = TRUE )

library(RAQSAPI)
library(sf)
library(phylin) #(idw)

#install.packages("keyring")

#keyring::has_keyring_support()

#library("keyring")  
#keyring::key_set(service = "AQSDatamart",
#                 username = "dad11493@colostate.edu")
#bolefox39 <- still seems to work (sent to csu email)
  # now throwing errors?

library(lubridate)
library(RAQSAPI)  
library(keyring)  

  aqs_credentials(username = "daniel.dean414@gmail.com",
                  key = "carmelwren37")
  
  # password = carmelwren37
    # oh--the issue is actually with `keywring` package; suppoed to keep track of API passwords, etc.
      # check that it's loaded on this computer, has right information, etc.


  # Loading Environmental Data
  
  
# METAR

library(zoo)

# should merge/save local versions

# METARs data (from DIA)

library(pmetar)
metar_get("KDEN")
# CO Air & Space actually has its own!
metar_get("KCFO")


### Time-intensive step (hourly weather data for ~2 years), so commenting out for now
########################################################

dia_metars <- metar_get_historical("KDEN", 
                                   start_date = "2020-11-30",
                                   end_date = "2023-12-31", 
                                   from = "iastate") %>%
  metar_decode()  

save(dia_metars, file = "01_raw_data/dia_metars.rda")



kcfo_metars <- metar_get_historical("KCFO", 
                                   start_date = "2020-11-30",
                                   end_date = "2023-12-31", 
                                   from = "iastate") %>%
  metar_decode()  

save(kcfo_metars, file = "01_raw_data/kcfo_metars.rda")



#########################################################

load("01_raw_data/dia_metars.rda")


dia_metars_daily_means <- dia_metars %>%
  mutate(Date = date(METAR_Date)) %>%
  group_by(Date) %>%
  dplyr::select(Airport_ICAO, Date, Day_of_Month, Wind_speed:Elevation) %>%
  mutate(smoke = as.numeric(str_detect(Weather_information, "Smoke"))) %>%
  dplyr::select(-c(Wind_direction,Visibility:Visibility_unit,
                   Cloud_coverage:Runway_visibility)) %>%
  mutate(across(where(is.numeric), ~mean(.x, na.rm = TRUE))) %>%
  unique()

save(dia_metars_daily_means,
     file = "01_5_processed_data/dia_metars_daily_means.rda")






load("01_raw_data/dia_metars.rda")


kcfo_metars_daily_means <- kcfo_metars %>%
  mutate(Date = date(METAR_Date)) %>%
  group_by(Date) %>%
  dplyr::select(Airport_ICAO, Date, Day_of_Month, Wind_speed:Elevation) %>%
  mutate(smoke = as.numeric(str_detect(Weather_information, "Smoke"))) %>%
  dplyr::select(-c(Wind_direction,Visibility:Visibility_unit,
                   Cloud_coverage:Runway_visibility)) %>%
  mutate(across(where(is.numeric), ~mean(.x, na.rm = TRUE))) %>%
  unique()

save(kcfo_metars_daily_means,
     file = "01_5_processed_data/kcfo_metars_daily_means.rda")

#########################

### OK, should also try and merge
  # AQS data is all, I think, hourly, although I think I got daily summaries via tha API
  # interestingly the AQS column formats are all compatible, so could merge rowwise if I wanted

  # OK, what columns are relevant?
    # date - "local date"
    # value = "arithmatic mean" even for 24-hr AQS measurements 
    # parameter (measurement should be noted, but isn't strictly needed)
    # maybe location? Also mostly relevant for context at this point

  # I guess can get rid of 'extra' variables across the board

library(janitor)


# OK, think I should use the nearer airport


rmss_bbox <- data.frame(latitude = 39.74039751943014,
                  longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("longitude", "latitude"), crs = "EPSG:6427") %>%
  st_buffer(dist = 0.75) %>%
  st_bbox()


so2_aqs_bbox <- aqs_dailysummary_by_box(parameter = "42401", 
                                             bdate = date_1,
                                             edate = date_2,
                                        minlon = rmss_bbox[[1]],
                                        maxlon = rmss_bbox[[3]],
                                        minlat = rmss_bbox[[2]],
                                        maxlat = rmss_bbox[[4]])

co_aqs_bbox <- aqs_dailysummary_by_box(parameter = "42101", 
                                        bdate = date_1,
                                        edate = date_2,
                                        minlon = rmss_bbox[[1]],
                                        maxlon = rmss_bbox[[3]],
                                        minlat = rmss_bbox[[2]],
                                        maxlat = rmss_bbox[[4]])

ozone_aqs_bbox <- aqs_dailysummary_by_box(parameter = "44201", 
                                       bdate = date_1,
                                       edate = date_2,
                                       minlon = rmss_bbox[[1]],
                                       maxlon = rmss_bbox[[3]],
                                       minlat = rmss_bbox[[2]],
                                       maxlat = rmss_bbox[[4]])

pm_10_aqs_bbox <- aqs_dailysummary_by_box(parameter = "81102", 
                                          bdate = date_1,
                                          edate = date_2,
                                          minlon = rmss_bbox[[1]],
                                          maxlon = rmss_bbox[[3]],
                                          minlat = rmss_bbox[[2]],
                                          maxlat = rmss_bbox[[4]])

pm_2_5_aqs_bbox <- aqs_dailysummary_by_box(parameter = "88101", 
                                          bdate = date_1,
                                          edate = date_2,
                                          minlon = rmss_bbox[[1]],
                                          maxlon = rmss_bbox[[3]],
                                          minlat = rmss_bbox[[2]],
                                          maxlat = rmss_bbox[[4]])

save(pm_2_5_aqs_bbox, file = "01_raw_data/pm_2_5_aqs_bbox.rda")
save(pm_10_aqs_bbox, file = "01_raw_data/pm_10_aqs_bbox.rda")
save(ozone_aqs_bbox, file = "01_raw_data/ozone_aqs_bbox.rda")
save(co_aqs_bbox, file = "01_raw_data/co_aqs_bbox.rda")
save(so2_aqs_bbox, file = "01_raw_data/so2_aqs_bbox.rda")

#worth checking  AQS smoke (11204) as well

smoke_aqs_bbox <- aqs_dailysummary_by_box(parameter = "11204", 
                                           bdate = date_1,
                                           edate = date_2,
                                           minlat = rmss_bbox[[1]],
                                           maxlat = rmss_bbox[[3]],
                                           minlon = rmss_bbox[[2]],
                                           maxlon = rmss_bbox[[4]])
  # yep, nothing there

# OK, so PM10 is the only one where I know they have weekly readings, but should check

  # I guess pick a single method in each case again?

pm_2_5_aqs_bbox %>% ggplot() + aes(x = as_date(date_local), y = arithmetic_mean) + facet_wrap(. ~ site_address) + geom_point()

# 2102 Athens  (1001 -- hopefully unique in context) seems worth removing; started partway into 2023
# also 12400 W. HWY 285 (0005)


  # whereas PM10 has 12 monitors (if with varying timeframes; one only starts in 2023)
  # ozone: 29; pretty wide range in sampling intervals, though
  # co: 8 monitors; one (Cheyenne soccer complex) is notably lower than others, misc. gaps
  # so2: 6 monitors, with one only starting in 2023 again; appreciable variation

# So, at least as a first thought, order of operations might be:
  # 1) Maybe exclude sites with large-enough gaps/missing periods (e.g. one starting in 2023)
  # 2) use MICE or some other imputing tool to fill in gaps where reasonable
  # 3) Use IDW to get a ~consensus reading after gaps are filled

  # so at least at the macro scale, only 2 sites that are mostly missing
    # site #1001, and #0005 (different counties, but appear to be unique)

  # from there, try imputing missing values?
    # probably have to cut down to arith, mean and pivot_wider
    # also pick a single standard/method per pollutant, I think
      # maybe then just get a per-date/site mean? Looks like different monitors differ

# somewhat arbitrary options: I guess aiming for shortest, latest standard
# PM2.5: "PM25 24-hour 2024"
# PM10: single standard, but fairly even split of 4 methods
# Ozone: "Ozone 8-hour 2015"; single method
# CO: "CO 1-hour 1971"; single method
# SO2: "SO2 1-hour 2010"; ~2:1 split 


library(mice)


epa_aqs_bbox_all <- rbind(pm_2_5_aqs_bbox,
                          pm_10_aqs_bbox, 
                          ozone_aqs_bbox,
                          co_aqs_bbox,
                          so2_aqs_bbox) %>%
  filter(pollutant_standard %in% c("PM25 24-hour 2024",
                                   "PM10 24-hour 2006",
                                   "Ozone 8-hour 2015",
                                   "CO 8-hour 1971",
                                   "SO2 1-hour 2010"
                                   )) 
  
save(epa_aqs_bbox_all, file = "01_5_processed_data/epa_aqs_bbox_all.rda")


load(file = "01_5_processed_data/epa_aqs_bbox_all.rda")



## OK new version with no ~unintended NAs, all dates accounted for, etc.:


epa_aqs_bbox_all_readings_minimal <- epa_aqs_bbox_all %>%
  mutate(site_unique = paste0("site_", county_code, "_", site_number),
         site_param = paste0(site_unique, "_", parameter_code)) %>%
  dplyr::select(site_unique,
                date_local,
                parameter,
                site_param,
                parameter_code,
                arithmetic_mean) %>%
  group_by(site_unique, parameter, date_local) %>%
  mutate(arithmetic_mean = mean(arithmetic_mean)) %>%
  unique() %>%
  data.frame()


epa_aqs_bbox_all_coords_minimal <- epa_aqs_bbox_all %>%
  mutate(site_unique = paste0("site_", county_code, "_", site_number),
         site_index = as.integer(as.factor(site_unique))) %>%
  dplyr::select(site_unique,
                site_index,
                latitude,
                longitude) %>%
  unique() %>%
  data.frame()



epa_aqs_date_placeholder <-expand.grid(
    date_local = seq.Date(from = min(as.Date(epa_aqs_bbox_all_readings_minimal$date_local)),
                          to = max(as.Date(epa_aqs_bbox_all_readings_minimal$date_local)), by = "day"),
    site_param = unique(epa_aqs_bbox_all_readings_minimal$site_param))


epa_aqs_date_placeholder_mice_interpolated <- epa_aqs_date_placeholder %>% 
  left_join((epa_aqs_bbox_all_readings_minimal %>%
               dplyr::select(site_param, 
                             date_local,
                             arithmetic_mean)) %>%
              mutate(date_local = as.Date(date_local))) %>% 
  group_by(site_param) %>% 
  mutate(na_105d_count = slide(arithmetic_mean, 
                               ~sum(as.numeric(is.na(.x))), 
                               .after = 105)) %>%
  unnest(na_105d_count) %>%
  mutate(max_na_105d_count = max(na_105d_count)) %>%
  filter(max_na_105d_count < 105 )  %>% 
  ungroup() %>% 
  dplyr::select(-contains("na")) %>%
  pivot_wider(values_from = arithmetic_mean,
              names_from = site_param) %>%
  mice() %>%
  complete(action  ="long") %>% 
  dplyr::select(-starts_with(".")) %>% 
  group_by(date_local) %>% 
  mutate(across(starts_with("site"), ~median(.x))) %>% 
  unique()%>% 
  pivot_longer(cols = starts_with("site"),
               names_to = "site_param",
               values_to = "arithmetic_mean") %>% 
  mutate(param = as.numeric(as.factor(str_extract(site_param, "\\d{5}$")))) 

save(epa_aqs_date_placeholder_mice_interpolated, file = "01_5_processed_data/epa_aqs_date_placeholder_mice_interpolated.rda")

# then add geometry, run IDW

epa_aqs_date_placeholder_mice_interpolated_idw <- epa_aqs_date_placeholder_mice_interpolated %>%
  mutate(site_unique = substr(site_param, start = 1, stop = 13),
         param = substr(site_param, start = 15, stop = 19)) %>%
   left_join(epa_aqs_bbox_all_coords_minimal, by = "site_unique") %>%
  group_by(date_local, param) %>%
  nest() %>%
  mutate(coords = purrr::map(.x = data, 
                             .f = ~.x[c("latitude","longitude")]),
         arith_mean = purrr::map(.x = data, 
                                 .f = ~.x['arithmetic_mean']),
         idw = purrr::map2(.x = coords, .y = arith_mean, 
                           .f = ~phylin::idw(values = unlist(.y),
                                             coords = data.frame(.x),
                                             grid = data.frame(latitude = 39.74039751943014,
                                                               longitude = -104.52398743305764))))  %>% 
  unnest(idw)

save(epa_aqs_date_placeholder_mice_interpolated_idw, file = "01_5_processed_data/epa_aqs_date_placeholder_mice_interpolated_idw.rda")

# reminder to merge with rest of data for downstream calculations

# let's go ahead and repeat with the 10-year PM2.5 data now to be sure methods match
  # do I want to keep the 105-day cutoff, or go with 10% to get ~1 year?
    # going by existing approach, seemed like random ~noise with 105 misisng days
      # Oh, also ensuring I should have roughly the same values *within* period of interest
        # or maybe filter by station IDs in the original set? 
        # because the latter might be *too* stringent now
```


# smoke data



# loading smoke data
```{r smoke_data}


library(tidyverse)
library(doParallel)
library(foreach)
library(parallel)


urlBase <- 'https://satepsanone.nesdis.noaa.gov/pub/FIRE/web/HMS/Smoke_Polygons/Shapefile'

#destfile <- "D:\\Desktop\\Environmental Data Science Course\\Smoke Polygons\\Polygons\\temp.zip"
#destfile <- "C:\\Users\\Admin\\Documents\\erhs_s_2022\\erhs_638\\02_code\\Smoke Polygons\\Polygons\\temp.zip"

destfile <- "temp.zip"
#destfile <- "C:\\Users\\Admin\\Documents\\erhs_s_2022\\erhs_638\\02_code\\lab_5_download_data"

dates <- seq.Date(from=as.Date("2020-11-30"),to=as.Date("2023-12-31"),by="day") 



# loop takes 2.5 minutes on my computer, downloads about 10 MB of data
system.time({
  
  smokepolys <- foreach(date = dates, .packages=c("sf","tidyverse"), .combine="rbind")%do%{ #file input/output usually can't be parallelized
    
    yyyy <- str_sub(date,1,4)
    mm <- str_sub(date,6,7)
    #dd <- str_sub(date,9,10)
    dt <- str_replace_all(date,pattern="-",replacement="")
    
    fileURL <- str_c(urlBase, yyyy, mm, str_c("hms_smoke",dt,".zip"), sep ="/")
    #destfile <- str_c(".\\Polygons\\temp.zip")
    destfile <- "temp.zip"
    
    try_error <- try(
      download.file(url=fileURL, destfile=destfile)
    )
    
    if( !(class(try_error) == "try-error") ){
      
      unzip(zipfile=destfile, 
            exdir=str_c(".\\Polygons\\hms_smoke",dt))
      file.remove(destfile)
      
      shape <- st_read(str_c(".\\Polygons\\hms_smoke",dt))
      
      if(identical(colnames(shape),c("Satellite","Start","End","Density","geometry"))){
        
        return( shape %>% 
                  mutate(Date = date))
        
      }else{
        
        return(NULL)
        
      }
      
      
      
    }else{
      
      return(NULL)
      
    }
    
  }
  
})#end system.time

save(x=smokepolys,file="US_HMSSmokePolygons_2020.RData")


# turning off spherical geometry?

sf::sf_use_s2(FALSE)

smokepolys_list <- smokepolys %>%
  group_by(Date) %>%
  group_split()

ncores <- parallel::detectCores()

cl <- makeCluster(ncores-1)
registerDoParallel(cl)

load("02_code/US_HMSSmokePolygons_2020.RData") # forgot to rename/direct from default

# if I wanted to do entire area with AQS monitors 
rmss_bbox <- data.frame(latitude = 39.74039751943014,
                        longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("latitude", "longitude"), crs = st_crs(smokepolys)) %>%
  st_buffer(dist = 0.75) %>%
  st_bbox()

# but at least for now, let's do a single point:
# remember CRS

rmss_point <- data.frame(latitude = 39.74039751943014,
                         longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("longitude", "latitude"), 
               crs = st_crs(smokepolys))

#man, this is messy (geo. agreement, etc.), but this works; also apparently
#doesn't need parallel processing

smokepolys_intersects <- smokepolys %>%
  mutate(intersect = as.numeric(st_covers((geometry),
                                          rmss_point, sparse = TRUE))) %>% 
  filter(!is.na(intersect))

ggplot() + geom_sf(aes(geometry = geometry, fill = Density), alpha = 0.05, color = 'grey', data = smokepolys_intersects) + geom_sf(aes(geometry = geometry), data = rmss_point, color = 'red') + theme_void() + facet_wrap(. ~ Density)

smokepolys_intersects$Density %>% table()

save(smokepolys_intersects, file= "01_5_processed_data/smokepolys_intersects.rda")

```

# incorporating smoke data with 10-year context on PM2.5:
```{r}
#oh, probably easier to replace date_1 with date_2 - 365*10
date_1 <- min(rmss_data_filtered$Date)-61 #days (to allow rolling summaries for earliest samples)
date_2 <- max(rmss_data_filtered$Date)

rmss_bbox <- data.frame(latitude = 39.74039751943014,
                        longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("longitude", "latitude"), crs = "EPSG:6427") %>%
  st_buffer(dist = 0.75) %>%
  st_bbox()
# a little larger than 50 km; I guess more conservative 

pm_2_5_aqs_bbox_10y <- aqs_dailysummary_by_box(parameter = "88101", 
                                               bdate = date_1 - 3653, # 10 years, rounding up
                                               edate = date_2,
                                               minlon = rmss_bbox[[1]],
                                               maxlon = rmss_bbox[[3]],
                                               minlat = rmss_bbox[[2]],
                                               maxlat = rmss_bbox[[4]])

save(pm_2_5_aqs_bbox_10y, file = "01_raw_data/pm_2_5_aqs_bbox_10y.rda")

load("01_raw_data/pm_2_5_aqs_bbox_10y.rda")

# Oh, need to get 10-year averages/summary stats; so replace date_1 with 2012_12_30

pm_2_5_aqs_bbox_10y_readings_minimal <- pm_2_5_aqs_bbox_10y  %>%
  filter(pollutant_standard == "PM25 24-hour 2024" & 
           event_type %in% 
           c("Concurred Events Excluded", "No Events") ) %>%
  mutate(site_unique = paste0("site_", county_code, "_", site_number),
         site_param = paste0(site_unique, "_", parameter_code)) %>%
  dplyr::select(site_unique,
                date_local,
                parameter,
                site_param,
                parameter_code,
                arithmetic_mean) %>%
  group_by(site_unique, parameter, date_local) %>%
  mutate(arithmetic_mean = mean(arithmetic_mean)) %>%
  unique() %>%
  data.frame()

# coordinates will be the same; should be able to cleanly exclude extras w/ left_join

  # OK also thinking most consistent approach is to use same set of stations, rather than a new inclusion criteria

############ 10-year data (for ~context on smoke data)

pm_2_5_aqs_bbox_10y_placeholder <-expand.grid(
    date_local = seq.Date(from = min(as.Date(pm_2_5_aqs_bbox_10y_readings_minimal$date_local)),
                          to = max(as.Date(pm_2_5_aqs_bbox_10y_readings_minimal$date_local)), by = "day"),
    site_param = unique(pm_2_5_aqs_bbox_10y_readings_minimal$site_param))


pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated <- pm_2_5_aqs_bbox_10y_placeholder %>% 
  filter(site_param %in% epa_aqs_date_placeholder_mice_interpolated$site_param) %>% # replacing ~contingent inclusion criteria
  left_join((pm_2_5_aqs_bbox_10y_readings_minimal %>%
               dplyr::select(site_param, 
                             date_local,
                             arithmetic_mean)) %>%
              mutate(date_local = as.Date(date_local))) %>% 

  pivot_wider(values_from = arithmetic_mean,
              names_from = site_param) %>%
  mice() %>%
  complete(action  ="long") %>% 
  dplyr::select(-starts_with(".")) %>% 
  group_by(date_local) %>% 
  mutate(across(starts_with("site"), ~median(.x))) %>% 
  unique()%>% 
  pivot_longer(cols = starts_with("site"),
               names_to = "site_param",
               values_to = "arithmetic_mean") %>% 
  mutate(param = as.numeric(as.factor(str_extract(site_param, "\\d{5}$")))) 


# then add geometry, run IDW

pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw <- pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated %>%
  mutate(site_unique = substr(site_param, start = 1, stop = 13),
         param = substr(site_param, start = 15, stop = 19)) %>%
   left_join(epa_aqs_bbox_all_coords_minimal, by = "site_unique") %>%
  group_by(date_local, param) %>%
  nest() %>%
  mutate(coords = purrr::map(.x = data, 
                             .f = ~.x[c("latitude","longitude")]),
         arith_mean = purrr::map(.x = data, 
                                 .f = ~.x['arithmetic_mean']),
         idw = purrr::map2(.x = coords, .y = arith_mean, 
                           .f = ~phylin::idw(values = unlist(.y),
                                             coords = data.frame(.x),
                                             grid = data.frame(latitude = 39.74039751943014,
                                                               longitude = -104.52398743305764))))  %>% 
  unnest(idw)


save(pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw,
     file = "01_5_processed_data/pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw.rda")


load("01_5_processed_data/smokepolys_intersects_10y.rda")
# version with full data (first round stopped too early for some reason)

load("../01_raw_data/US_HMSSmokePolygons_2010_2023.RData")
  # still called 'smokepolys' so should run normally from here

  # looks like longitude and latitude are flipped at least vs convention below
  # any good way to reverse manually?
    # huh; the buffer does seem to plot correctly 
    # although I think `dist` is in meters instead of degrees


rmss_buffer <- data.frame(latitude = 39.74039751943014,
                         longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("longitude", "latitude"), 
               crs = st_crs(smokepolys)) %>%
  st_buffer(dist = 6000)

smokepolys_intersects_10y <- smokepolys[st_is_valid(smokepolys),]%>%
  mutate(intersect = as.numeric(st_intersects((geometry),
                                              rmss_buffer, sparse = TRUE))) %>%
  filter(!is.na(intersect))#

  # warning about bounding boxes, but checks out, I think

save(smokepolys_intersects_10y, file = "../01_5_processed_data/smokepolys_intersects_10y_new.rda")



# oh, wait--approach below will have missing values for non-smoke-exposed days; have to accomodate that

smoke_exposure_pm25_10y <- pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw[!(pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw$date_local %in%
                                                          smokepolys_intersects_10y$Date),] %>%
  mutate(date_local = as.Date(date_local),
         month = month(date_local)) %>%
  mutate(season = case_when(
    month %in% 1:3 ~ "Winter",
    month %in% 4:6 ~ "Spring",
    month %in% 7:9 ~ "Summer",
    month %in% 10:12 ~ "Fall"
  )) %>%
  group_by(season) %>%
  mutate(seasonal_mean = mean(Z)) %>%
  ungroup() %>%
  group_by(month) %>%
  unique() %>%
  mutate(monthly_mean = mean(Z)) %>%
  dplyr::select(season, month, seasonal_mean, monthly_mean) %>%
  unique() %>%
    #right_join((epa_aqs_date_placeholder_mice_interpolated_idw %>%
  right_join((pm_2_5_aqs_bbox_10y_placeholder_mice_interpolated_idw %>%
                 dplyr::select(date_local, param, Z) %>%
                 filter(param == "88101") %>%
                  mutate(month = lubridate::month(date_local))),
              by = 'month') %>%
    dplyr::mutate(diff_pm_2_5_season = Z - seasonal_mean,
                  diff_pm_2_5_month = Z - monthly_mean) %>% 
  ungroup() %>%
    dplyr::select(date_local, Z, seasonal_mean, diff_pm_2_5_season, diff_pm_2_5_month) %>% 
    unique() %>%
  mutate(hms_plume = (date_local %in% smokepolys_intersects_10y$Date)) %>%
    mutate(smoke_pm_2_5_season = case_when(diff_pm_2_5_season <0 ~ 0,
                                           hms_plume == FALSE ~ 0,
                                           diff_pm_2_5_season > 0 & hms_plume == TRUE ~ diff_pm_2_5_season),
           smoke_exposed_season= smoke_pm_2_5_season > 0) %>%
  mutate(smoke_pm_2_5_month = case_when(diff_pm_2_5_month <0 ~ 0,
                                         hms_plume == FALSE ~ 0,
                                         diff_pm_2_5_month > 0 & hms_plume == TRUE ~ diff_pm_2_5_month),
         smoke_exposed_month = smoke_pm_2_5_month > 0)  


save(smoke_exposure_pm25_10y, file = "../01_5_processed_data/smoke_exposure_pm25_10y_new.rda")

```



# I'm pretty sure this block is all vestigial, but leaving for now in case I missed dependencies, etc.

```{r}

# I think this function is vestigial now, but leaving in just in case
  
nullToNA <- function(x) {
  x[sapply(x, is.null)] <- NA
  return(x)
}

# need a per-day summary of smoke data for merging
  # I guess need to add binary 'smoke day' downstream, since this only has days with smoke

  # losing information on ~ density identities of plumes

load(file = "../01_5_processed_data/smokepolys_intersects.rda")
#load(file = "../01_5_processed_data/smoke_1sd_indicators_data.rda") # functionally identical, but I guess more ~rigorous

smokepolys_intersects_clean <- smokepolys_intersects %>% 
  st_drop_geometry() %>% 
  clean_names() %>%
  mutate(density = factor(density, levels = c("Light", "Medium", "Heavy")))  %>% 
  dplyr::select(date, density) %>% 
  group_by(date) %>% 
  mutate(plume = 1) %>% 
  pivot_wider(names_from = density, values_from = plume) %>%
  mutate(plumes_light = length(Light[[1]]),
         plumes_medium = length(Medium[[1]]),
         plumes_heavy = length(Heavy[[1]]),
         plumes_smoke = sum(plumes_light,
                            plumes_medium,
                            plumes_heavy)) %>%
  dplyr::select(date, plumes_light:plumes_smoke) %>%
  unique()

# adding the more stringent smoke indicator

load(file = "../01_5_processed_data/kcfo_metars_daily_means.rda")
load(file = "../01_5_processed_data/epa_aqs_bbox_all_simple.rda")
load(file = "../01_5_processed_data/epa_aqs_bbox_all_idw_repaired.rda")
load(file = "../01_5_processed_data/epa_aqs_bbox_all_comb.rda")

  # huh, so the IDW version has 213 fewer values; what would be going on there?
    # so, same dates as far as I can tell?


# OK, think it seems justifiable to merge (right merge?) replacing missing IDW with simple means

epa_aqs_bbox_all_idw %>% dplyr::select(date_local, parameter_code) %>% table() %>% data.frame() %>% pivot_wider(names_from = parameter_code, values_from = Freq) %>% summary()
  # relevant summary: 42401 (SO2?) is 99.62% accounted for, 81102 (PM10) is 79.3% accounted for

  # example where I want only new rows from `test_df2`, and keep all from `test_df1` (smaller dataset)
  #full_join(test_df1, test_df2[!(test_df2$key %in% test_df1$key),])

    # a bit more involved by using 2 columns, but solution below seems to match row # discrepancy (213)

#epa_aqs_bbox_all_comb <- epa_aqs_bbox_all_idw %>%
#  dplyr::rename(am_mean = "Z") %>%
#  full_join(epa_aqs_bbox_all_simple[!(paste0(epa_aqs_bbox_all_simple$date_local, #epa_aqs_bbox_all_simple$parameter_code) %in%
#                                        paste0(epa_aqs_bbox_all_idw$date_local, epa_aqs_bbox_all_idw$parameter_code)),])
  # OK, now # of rows matches



# so, to summarize steps;
  # 1) ID all AQS monitors within ~60 miles (0.75 degrees)
  # 2) remove monitors with >10% missing data
  # 3) Perform an arithmetic mean where multiple readings were collected per day
  # 3)  Use ~multiple interpolation (MICE) to replace remaining missing values by date
  # 4) Where there are enough monitors for a day-metric combination to support inverse distance-weighted averaging, use IDW to obtain averages weighted for the RMSS location
  # 5) In cases where IDW could not be accomplished (e.g. 1 station), use station value or simple mean of available stations
```



# OK, load in the two latest files, and see how names/structures match

```{r}

getwd()

# new files; reformat to match expected inputs (get rid of extra columns, etc.)
  # AQS data -- shoudn't be too different, but more ~consistent handling of NAs, MICE
  # OK, reloading version with median of 5 MICE runs for `complete` instead of default 1-run extraction
load(file = "../01_5_processed_data/epa_aqs_date_placeholder_mice_interpolated_idw.rda")

epa_aqs_bbox_all_comb_NEW <- epa_aqs_date_placeholder_mice_interpolated_idw %>%
  dplyr::select(date_local, param, Z) %>%
  rename(parameter_code = param,
         am_mean = Z) %>%
  ungroup()

  # smoke data -- latest version (w/ PM2.5-based values); should be same methodology as above
load("../01_5_processed_data/smoke_exposure_pm25_10y.rda")
smoke_exposure_NEW <- smoke_exposure_pm25_10y %>%
  ungroup() %>%
  dplyr::select(date_local, hms_plume,
                smoke_exposed_season, smoke_exposed_month, 
                smoke_pm_2_5_season, smoke_pm_2_5_month)


###

# 4 missing dates from METAR data; filling in seems reasonable in that it's just the one station, not likely to be huge ~spikes
  # also realized `complete` only looks at 1st iteration by default, so taking mean (maybe median?) of outputs
    # inputs looked pretty reasonable on AQS (maybe b/c more columns?), but should do that to be more thorough

kcfo_metars_daily_means_mice <- (((kcfo_metars_daily_means %>% 
                                     dplyr::filter(!is.na(Date)) %>% 
                                     dplyr::select(Date, Temperature, Dew_point) %>% 
                                     right_join(data.frame(
                                       Date = seq.Date(from = min(kcfo_metars_daily_means$Date, 
                                                                  na.rm = TRUE), 
                                                       to = max(kcfo_metars_daily_means$Date, 
                                                                na.rm = TRUE),
                                                       by = 'day')))))) %>% 
  mice() %>% complete(action = 'long') %>% 
  data.frame() %>% 
  group_by(Date) %>% 
  mutate(Temperature = median(Temperature),
         Dew_point = median(Dew_point)) %>% 
  dplyr::select(Date, Temperature, Dew_point) %>% 
  unique()

# OK! *Some* NAs are expected because the KCFO data is loaded to the nearest month/year, so extra dates
api_env_data_61d_prelag_NEW <- kcfo_metars_daily_means_mice %>%
  #dplyr::select(Date, Temperature, Dew_point) %>%
  #mutate(rhi = humidity::RH(t = Temperature, Td = Dew_point, isK = FALSE)) %>%
  mutate(heat_index = weathermetrics::heat.index(t = Temperature, dp = Dew_point, temperature.metric = "celsius", output.metric = "celsius", round = 1)) %>%
  clean_names() %>%
  mutate(date = lubridate::as_date(date)) %>%
  right_join((
    #epa_aqs_bbox_all_simple %>%
    epa_aqs_bbox_all_comb_NEW %>%
      pivot_wider(names_from = "parameter_code",
                  values_from = "am_mean") %>%
      mutate(date_local = lubridate::as_date(date_local)) %>%
      dplyr::rename(pm_2_5 = 2,
                    pm_10 = 3,
                    o3 = 4,
                    co = 5,
                    so2 = 6,
                    date = date_local))) %>%
  left_join(smoke_exposure_NEW, by = c('date' = 'date_local')) %>%
  #mutate(across(contains(c("smoke", "plume")), ~replace_na(.x, 0))) %>%
  ungroup() %>%
  mutate(smoke_day = as.numeric(hms_plume)) # 'legacy' metric for raw presence/absence of HMS plumes

  # in lagged data, should be 61 NAs (corresponding to 'buffer' preceding 1st bull sample)

api_env_data_61d_lag_NEW <- api_env_data_61d_prelag_NEW %>%
  #left_join(smoke_1sd_indicators_data, by = c("date" = "date_local")) %>%
  #mutate(smoke_impacted_plume = as.numeric(smoke_impacted_plume)) %>%
  mutate(across(all_of(c("temperature", "dew_point", "heat_index", "pm_2_5",
                         "pm_10", "o3", "co", "so2", "smoke_pm_2_5_season", "smoke_pm_2_5_month")), 
                list(median_61d = ~as.numeric(nullToNA(slide(.x, 
                                                             ~median(.x, na.rm = TRUE),
                                                             .before =61, 
                                                             .complete = FALSE)))))) %>% 

  mutate(across(all_of(c("smoke_day", "smoke_exposed_season", "smoke_exposed_month"
                         )), 
                list(sum_61d = ~as.numeric(nullToNA(slide(.x, 
                                                    ~sum(.x, na.rm = TRUE),
                                                    .before =61, 
                                                    .complete = FALSE)))))) 
                                       
  # Switching `.complete` to FALSE; 'buffer' dates won't be included anyway

save(api_env_data_61d_lag_NEW, file = "../01_5_processed_data/api_env_data_61d_lag_NEW.rda")
  # OK, so from here, use this in the model, and switch to LME4 
  # looks correct 


  # using right_join becasue we're only interested in dates with associated bull samples

rmss_with_api_env_data_61d_lag_NEW <- api_env_data_61d_lag_NEW %>%
  right_join((rmss_data_filtered %>% 
                ungroup() |>
                dplyr::mutate(sample_id = row_number()) |>
                dplyr::filter(!is.na(Sts)) %>% # two ~one-off missing statuses from original data
                clean_names() %>%
                dplyr::select(date, 
                              bull_code, sample_id,
                              sts)), by = "date") %>%
  mutate(discard = sts == "Disc",
         pass = sts == "Pend") %>%
                                         mutate(breed = as.factor(
                                           str_extract(bull_code, "[A-Z]{2}"))) %>%
                                         mutate(angus = as_factor(str_detect(breed, "A"))) #%>%
  #group_by(bull_code) %>%
  #mutate(smoke_impacted_plume_cumulative = sum(smoke_impacted_plume, na.rm = TRUE))

    # OK, realized cumulative exposure is trickier than I thought; 
      # requires fairly strong assumptions, I think
      # would need to have a stronger sense of how permanently the bulls are at the facility
        # if they're basically born and live there, could just track smoke days since DOB
        # if not, honestly not much difference vs current approach 

save(rmss_with_api_env_data_61d_lag_NEW, file = "../01_5_processed_data/rmss_with_api_env_data_61d_lag_NEW_update.rda")
  #what does HI stand for again here?
    # oh, heat index


# lower bull inclusion threshold

#load(file = "../01_5_processed_data/rmss_data_filtered_61d.RData")

load(file = "../01_5_processed_data/rmss_data_filtered_CODED.RData")
  # version w/ technician comments

#########3
# OK, adding unique sample names to enable sorting
  # should be 'final' version, so can use compatibly

rmss_with_api_env_data_61d_lag_61d_NEW_bulls <- api_env_data_61d_lag_NEW %>%
  right_join((rmss_data_filtered %>% 
                ungroup() |>
                clean_names() %>%
                dplyr::mutate(sample_id = row_number()) |>
                dplyr::select(date, 
                              bull_code, sample_id,
                              sts)), by = "date") %>%
  mutate(discard = sts == "Disc",
         pass = sts == "Pend") %>%
                                         mutate(breed = as.factor(
                                           str_extract(bull_code, "[A-Z]{2}"))) %>%
                                         mutate(angus = as_factor(str_detect(breed, "A")))
                                       
# OK, even though 'out of order' in this form, sample IDs by row# are appleid upstream, so should match rmss_data_filtered

save(rmss_with_api_env_data_61d_lag_61d_NEW_bulls, file = "../01_5_processed_data/rmss_with_api_env_data_61d_NEW_lag.rda")
  # another ~20 bulls make the cut with 61 previous days
    # saved over previous version

# setting up version(s) with ages

library(openxlsx)
bull_bd <- read.xlsx("../01_raw_data/Bull listing with BD.xlsx",
                    detectDates = TRUE)

# so I'm filtering out unrecorded dates; might want to leave option to e.g. interpolate open
  # oh, need to think through how to get valid median; think `case_when` wouldn't really catch it 
    # also could consider first instance of sampling?

  # OK, I think the `failed to parse' warnings are just about the known missing birthdates
  # OK, but 27 'NA' birthdates apparently not covered by the 3052 `missing` ones and/or conditionals 
rmss_with_api_env_data_61d_lag_NEW_ages <- rmss_with_api_env_data_61d_lag_NEW %>%
  left_join(bull_bd, by = c("bull_code" = "Bull.ID"))  %>% 
  mutate(missing = !str_detect(Birthdate, "\\d" ) | is.na(Birthdate)) %>% 
  mutate(Birthdate =  lubridate::ymd(Birthdate),
         Birthdate = case_when(
           missing == TRUE ~ median(Birthdate, na.rm = TRUE),
           missing == FALSE ~ Birthdate
         )) %>%
  clean_names() %>%
  mutate(age = (date - birthdate)/365)

#rmss_with_api_env_data_61d_lag_NEW_ages <- unique(rmss_with_api_env_data_61d_lag_NEW_ages)

save(rmss_with_api_env_data_61d_lag_NEW_ages, file = "../01_5_processed_data/rmss_with_api_env_data_61d_lag_NEW_ages_W_sample_ids.rda")

# Huh--apparently ending up w/ non-unique rows?
  # 

```

###################################### MODELS  ##################################
# Keeping 'old' models below for now for reference, but seemed cleaner to make a new set
  # also exploring thought about date as a random effect, option to model PM2.5-attr. smoke
  # sensitivity analysis last time showed similar effects for known vs imputed ages; maybe add those as a block below
  # Maybe more natural to have primary-only vs interactive effects in each block?

First set: PM2.5 Only
```{r}
library(lme4)
library(splines)

mod_q1 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q1_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
# slightly better AIC with date as a random effect; very little impact on estimates (probably within standard error)

# lower AIC without a breed-by-heat index interaction -- should use that as ~standard going forward

mod_q1_int1 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q1_rdate_int1 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

# oh, random effect for date does give better R^2, AIC; nothing really changes outside margin of error, though.

```


Set 2: Smoke + PM2.5

```{r}


mod_q2 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d+  ns(heat_index_median_61d) + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q2_rdate <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
# slightly better AIC with date as a random effect; very little impact on estimates (probably within standard error)

# lower AIC without a breed-by-heat index interaction -- should use that as ~standard going forward

mod_q2_int1 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q2_rdate_int1 <- glmer(discard ~ pm_2_5_median_61d+  smoke_exposed_season_sum_61d + smoke_exposed_season_sum_61d*angus + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

# pm2.5 AND smoke interactions


mod_q2_int1 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q2_rdate_int1 <- glmer(discard ~ pm_2_5_median_61d+  smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus+ (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
#



```



Model 3 (above plus additional air quality metrics)


```{r}
mod_q3 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d+  ns(heat_index_median_61d) + angus + age + pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d+ (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q3_rdate <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
# slightly better AIC with date as a random effect; very little impact on estimates (probably within standard error)

# lower AIC without a breed-by-heat index interaction -- should use that as ~standard going forward

mod_q3_int1 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q3_rdate_int1 <- glmer(discard ~ pm_2_5_median_61d+  smoke_exposed_season_sum_61d + smoke_exposed_season_sum_61d*angus + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

# pm2.5 AND smoke interactions


mod_q3_int1 <- glmer(discard ~ pm_2_5_median_61d + smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q3_rdate_int1 <- glmer(discard ~ pm_2_5_median_61d+  smoke_exposed_season_sum_61d + pm_2_5_median_61d*smoke_exposed_season_sum_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus+ (1|bull_code) + (1|bull_code:date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

```

```{r}

mod_q3 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d+ angus + age+  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q3_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
# slightly better AIC with date as a random effect; very little impact on estimates (probably within standard error)

mod_q3_int1 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d  + (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q3_int2 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + smoke_exposed_season_sum_61d*pm_2_5_median_61d +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d +  (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))



mod_q3_rdate_int2 <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + smoke_exposed_season_sum_61d*pm_2_5_median_61d +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d +  (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


```

scaled versions 
```{r}


mod_q1_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))))  ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q1_int1_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age +pm_2_5_median_61d*angus + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))))  ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q2_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d+ angus + age+  (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))))  ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_q2_int2_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + smoke_exposed_season_sum_61d*pm_2_5_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))))  ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))



mod_q3_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d+ angus + age+  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x)))) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))



mod_q3_int1_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d +  (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

mod_q3_int2_scaled <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus + smoke_exposed_season_sum_61d*pm_2_5_median_61d +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d +  (1|bull_code),
                               family = binomial('logit'),
                               data = (rmss_with_api_env_data_61d_lag_NEW_ages %>% mutate(across(is.numeric, ~scale(.x))) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


```





##########################################################################################
######### I don't think this table is final version #############

## Summary tables (can't seem to find code w/ grep, etc., so seeing if I can recreate)
  # wanting to make sure I'm reflecting latest inclusion criteria
  
Table 2 (1 is env. conditions -- should be unchanged by inclusion criteria)

```{r}
tbl_2 <- (rmss_with_api_env_data_61d_lag_NEW_ages__prov_final %>%
  mutate(Breed = case_when(breed == "XB" ~"Beef Crossbred",
                             breed == "SM" ~ "Simmental",
                             breed == "CH" ~ "Charolais",
                             breed == "AN" ~ "Angus",
                             breed == "AR" ~ "Red Angus")) %>%
  mutate(age = as.numeric(age)) %>% 
  dplyr::select(-breed) %>%
  group_by(Breed) %>% 
  mutate(`Samples (n)` = n()) %>%
  dplyr::select(Breed, bull_code, angus, age, `Samples (n)`, discard) %>% 
  unique() %>%
  group_by(Breed) %>%
  mutate(across(where(is.numeric),
                ~round(.x, 2))) %>% 
  rename(`Breed Group` = angus) %>%
  mutate(`Breed Group` = case_when(`Breed Group` == TRUE ~ "British",
                                   `Breed Group` == FALSE ~ "Continental")) %>% 
  mutate(`Bulls (n)` = n_distinct(bull_code),
         `Age (Yr); median (min, max)` = paste0(median(age),
                                                " (", min(age), ", ",
                                                max(age), ")"),
         `Discarded Samples (%)` = 100*(sum(as.numeric(discard))/n())) %>%
  dplyr::select(-age, -discard, -bull_code) %>%
  unique()) %>%
  rbind(
    rmss_with_api_env_data_61d_lag_NEW_ages__prov_final %>%
    mutate(age = as.numeric(age)) %>% 
    mutate(`Samples (n)` = n()) %>%
    dplyr::select(bull_code, age, `Samples (n)`, discard) %>% 
    unique() %>%
    mutate(across(where(is.numeric),
                  ~round(.x, 2))) %>% 
    mutate(`Bulls (n)` = n_distinct(bull_code),
           `Age (Yr); median (min, max)` = paste0(median(age),
                                                  " (", min(age), ", ",
                                                  max(age), ")"),
           `Discarded Samples (%)` = 100*(sum(as.numeric(discard))/n())
          ) %>%
    dplyr::select(-age, -discard, -bull_code) %>%
    unique() %>% 
      mutate(`Breed Group` = "-", Breed = "All",) %>%
      relocate(c(Breed, `Breed Group`),
               .before = `Bulls (n)`)
  ) %>%
  mutate(across(where(is.numeric),
                ~round(.x, 2))) %>% 
  relocate(`Samples (n)`, .before = `Discarded Samples (%)`)

write_csv(tbl_2, file = "../03_output/tbl_2_FILTERED.csv")


```

#######################################################33

# OK, think I realized the 'repeated samples' are actually groups of individuals given ~umbrella IDs 
  (all with >1 sample are also the ones with 'multiple' result in dates)
  
  # feeling most prudent to remove those at least until I hear back from Russ
  
  # I think that would make date and bull_id effectively synonymous
  
  # OK, and the scaling factors I worked out are:
    # O3: *100  <- report as 100 ppm (100 parts per million)
    # SO2, CO: * 10 (partially for uniformity) (10 parts per million)
    # Oh, double check if age is in days or years; it should be the latter
  

# Think 'main' analysis should use only known ages, and sensitivity analysis with interpolated ages
  # n = 99 for known ages, 102 for interpolated
```{r provisional 'final' models}

rmss_with_api_env_data_61d_lag_NEW_ages__prov_final <- rmss_with_api_env_data_61d_lag_NEW_ages %>%
filter(!str_detect(bull_code, "20\\d{2}")) %>%
  mutate(across(contains(c("so2", "co")) & !contains(("code")),
                   .fns = ~.x*10)) %>%
  mutate(across(contains(c("o3")),
                .fns = ~.x*100)) %>%
  filter(missing == FALSE) #%>%
 # unique()

#!!! OK, vaguely remembering that 'unique' isn't used here for a reason, but trying to confirm that
  # think it's something like unique identifying features being dropped upstream of model
    # OK, as a sanity check, seems non-coincidental that there are same number of rows in `rmss_data_filtered`?
      # weird, that one actually loses ~6 rows to `unique`



# seems like these may actually be ~inextricable groups of individuals
    # already inferred avg. age here, so remaining unique IDs can be retained


rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages <- rmss_with_api_env_data_61d_lag_NEW_ages %>%
filter(!str_detect(bull_code, "20\\d{2}")) %>%
  mutate(across(contains(c("so2", "co")) & !contains(("code")),
                   .fns = ~.x*10)) %>%
  mutate(across(contains(c("o3")),
                .fns = ~.x*100)) #%>%
  #filter(missing == FALSE)

```


# 'normal' models
```{r}
### Model 1

mod1_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod1_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age  + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod1_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age +  (1|bull_code) + pm_2_5_median_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod1_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))






### Model 2


mod2_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod2_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d + angus + age  + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod2_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age +  (1|bull_code) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod2_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d + angus + age + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


### Model 3

mod3_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d+ angus + age+  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod3_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod3_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod3_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

```




# interpolated ages

```{r}
### Model 1

mod_i1_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i1_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age  + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod_i1_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age +  (1|bull_code) + pm_2_5_median_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i1_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + angus + age + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))






### mod_iel 2


mod_i2_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i2_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d + angus + age  + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod_i2_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age +  (1|bull_code) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i2_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


### mod_iel 3

mod_i3_primary <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d+ angus + age+  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i3_primary_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

mod_i3_interactions <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + angus + age +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))


mod_i3_interactions_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d+angus + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|date) + pm_2_5_median_61d*angus + smoke_exposed_season_sum_61d*angus,
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final_interp_ages) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

```

saving
```{r}

save(mod1_primary_rdate, mod1_interactions_rdate, mod2_primary_rdate, mod2_interactions_rdate, mod3_primary_rdate, mod3_interactions_rdate, file = "final_models_update.RData")


```

# Sensitivity analysis: Removing breed terms
  # realizing these are going to be identical (no more breed to have interactions), so can collapse

```{r}
### mod_nb_el 1

mod_nb_1_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + age  + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
### model 2


mod_nb_2_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) + smoke_exposed_season_sum_61d + age +  (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))

### mod_nb_el 3

mod_nb_3_rdate <- glmer(discard ~ pm_2_5_median_61d + ns(heat_index_median_61d) +  smoke_exposed_season_sum_61d + age  +  pm_10_median_61d + o3_median_61d + co_median_61d +  so2_median_61d + (1|bull_code) + (1|date),
                               family = binomial('logit'),
                               data = ((rmss_with_api_env_data_61d_lag_NEW_ages__prov_final) ), nAGQ = 0 ,
                               control = glmerControl(optimizer = "Nelder_Mead", 
                                                      optCtrl = list(maxfun=2e5)))
###############

```

saving
```{r}

save(mod_nb_1_rdate, mod_nb_2_rdate, mod_nb_3_rdate, file = "final_models_nb_updated.RData")


```

###########3


# summary table

```{r}

# should have right order of parameter names now; still trying to see how to override default model labels

sjPlot::tab_model(mod1_primary_rdate, mod1_interactions_rdate, mod2_primary_rdate, mod2_interactions_rdate, mod3_primary_rdate, mod3_interactions_rdate, show.intercept = F, show.loglik = T, pred.labels = c("PM2.5 (61-Day Median; ug/m3)", "Heat Index (61-Day Median; nonlinear)", "Breed (British)", "Age (years)", "PM2.5-by-Breed Interaction (British)", "Smoke Days (61-Day Sum)", "Smoke-by-Breed Interaction (British)",  "PM10 (61-Day Median; ug/m3)", "Ozone (61-Day Median; 100 ppm)", "Carbon Monoxide (61-Day Median; 10 ppm)", "Sulfur Dioxide (61-Day Median; 10 ppm"), bootstrap = F, show.aic = T)

```

# without breed

```{r}

# should have right order of parameter names now; still trying to see how to override default model labels

sjPlot::tab_model(mod_nb_1_rdate, mod_nb_2_rdate, mod_nb_3_rdate, show.intercept = F, show.loglik = T, pred.labels = c("PM2.5 (61-Day Median; ug/m3)", "Heat Index (61-Day Median; nonlinear)", "Age (years)", "Smoke Days (61-Day Sum)",  "PM10 (61-Day Median; ug/m3)", "Ozone (61-Day Median; 100 ppm)", "Carbon Monoxide (61-Day Median; 10 ppm)", "Sulfur Dioxide (61-Day Median; 10 ppm"), bootstrap = F, show.aic = T)

```


# Figured out how to do facetting (just need to create a new dataframe from predictions, etc.)

```{r}
data.frame(prediction = as.numeric(predict(mod2_interactions_rdate, type = "response")), observed = mod2_interactions_rdate@frame$discard, breed_group = as.factor(mod2_interactions_rdate@frame$angus)) %>% mutate(observed = case_when(observed == TRUE ~ "Discard", observed == FALSE ~ "Pending"), breed_group = case_when(breed_group == TRUE ~ "British", breed_group == FALSE ~ "Continental")) %>% ggplot() + geom_density(aes(x = prediction, color = observed)) + theme_minimal() +scale_color_manual(values = c("red4", "cyan3")) + labs(x = "Predicted Discard Probability", y = "Density (Observations)", color = "True Sample Outcome")

data.frame(prediction = as.numeric(predict(mod2_interactions_rdate, type = "response")), observed = mod2_interactions_rdate@frame$discard, breed_group = as.factor(mod2_interactions_rdate@frame$angus)) %>% mutate(observed = case_when(observed == TRUE ~ "Discard", observed == FALSE ~ "Pending"), breed_group = case_when(breed_group == TRUE ~ "British", breed_group == FALSE ~ "Continental")) %>% ggplot() + geom_density(aes(x = prediction, color = observed)) + theme_minimal() +scale_color_manual(values = c("red4", "cyan3")) + labs(x = "Predicted Discard Probability", y = "Density (Observations)", color = "True Sample Outcome") + facet_wrap(. ~ breed_group, nrow = 2)

```



OK, Visualizations; think Wilcoxon tests don't carry much extra information


# summary models;

```{r}

# PM2.5 + smoke

ggplot() +
    aes(y = 100*(predict(mod2_interactions_rdate,
                         type = "response")),
        x = mod2_interactions_rdate@frame$pm_2_5_median_61d) +
    geom_vline(color = 'grey70', xintercept = as.numeric(quantile(mod2_interactions_rdate@frame$pm_2_5_median_61d, probs = c(0.025, 0.975)))) +
    #geom_point(aes(shape = (mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE",
    geom_point(aes(color = mod2_interactions_rdate@frame$smoke_exposed_season_sum_61d),
               alpha  = 0.5, size = 1.5) +
    geom_smooth(color = 'black', aes(linetype = mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE", "Continental" = "FALSE")),
                se = FALSE) +
    geom_smooth(linewidth = 1.5, color = "black", se = FALSE) +
    scale_color_viridis_c(option = 'viridis', direction = -1) + 
  #scale_linetype_manual(values = c(1,3)) +
    #scale_color_manual(values = c("#6ca7dfff", "#ffe88aff")) +
    theme_minimal() +
    labs(
        #title = "Predicted Sample Discard Probability",
        x = "Median 61-Day PM2.5 (ug/m3)",
        y = "Sample Discard Probability (%)",
        linetype = "Breed Group",
        color = "Smoke Days\n (of 61)") 

# by outcome
ggplot() +
    aes(y = 100*(predict(mod2_interactions_rdate,
                         type = "response")),
        x = mod2_interactions_rdate@frame$pm_2_5_median_61d) +
  geom_vline(color = 'grey70', xintercept = as.numeric(quantile(mod2_interactions_rdate@frame$pm_2_5_median_61d, probs = c(0.025, 0.975)))) +
    #geom_point(aes(shape = (mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE",
    geom_point(aes(
      #color = mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE", "Continental" = "FALSE"),
      color = mod2_interactions_rdate@frame$discard %>%
                       as.factor() %>%
                       forcats::fct_recode("Discard" = "TRUE", "Pending" = "FALSE")),
               alpha  = 0.5, size = 1.5) +
#    geom_smooth(aes(color = mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE", "Continental" = "FALSE")),
#                se = FALSE) +
      geom_smooth(color = 'black', aes(linetype = mod2_interactions_rdate@frame$angus %>% forcats::fct_recode("British" = "TRUE", "Continental" = "FALSE")),
                se = FALSE) +
    geom_smooth(linewidth = 1.5, color = "black", se = FALSE) +
    scale_color_manual(values = c('cyan4', 'red2')) +
    #scale_color_manual(values = c("#ffe88aff", "#63a2ddff")) +
    theme_minimal() +
    labs(
        #title = "Predicted Sample Discard Probability",
        x = "Median 61-Day PM2.5 (ug/m3)",
        y = "Sample Discard Probability (%)",
      #  color = "Breed Group",
        linetype = "Breed Group",
        color = "Sample Status") 


```


# map


```{r}


library(devtools)
library(tidyterra)
library(maptiles)

load("../01_5_processed_data/smokepolys_intersects.rda")

# note: EPSG:6427 is in meters, so doesn't match at least `mapView`; try `WGS84` or `EPSG:4326
  # oh, also should confirm that HMS data behaves how I expect
  # OK, 3 monitors (2 PM10, one ozone) at least nominally included outside boundary for 0.75 degrees

#library(basemapR)

load(file ="../01_5_processed_data/epa_aqs_bbox_all.rda")


library(maptiles)
osm_tiles <- get_tiles(x = (epa_aqs_bbox_all %>%
                          dplyr::select(latitude, longitude) %>%
                            unique() %>%
                          rbind(data.frame(latitude = 39.74039751943014,
                             longitude = -104.52398743305764)) %>% 
                          st_as_sf(coords = c("longitude", "latitude"),
                                   crs = "WGS84")),
                       provider = "CartoDB.Positron", 
                       zoom = 10,
                       crop = TRUE)

smokepoly_tiles <- get_tiles(x = smokepolys_intersects,
                             crop = TRUE,
                             provider = "CartoDB.Positron")
    # zoom = 10 seems about right; maybe could go a bit higher?
      # loading rime goes up appreciable after ~10
        # resolution appears a bit iffy
        # renders as really pixelated even with larger export image
# takes a bit to run with original zoom (presumably higher = more detail?)
  # huh--looks way too big as well? Includes most of New Mexico, for instance.
    # Oh, the points show up correctly when I combine--issue is that I guess zoom=5 tiles are just huge

# basic example 
#plot(osm_tiles)

#(epa_aqs_bbox_all %>%
#    dplyr::select(latitude, longitude) %>%
#    st_as_sf(coords = c("longitude", "latitude"),
#             crs = "WGS84")) %>% 
#  plot( add = T)

# comes out noticeably pixelated, which increases with a higher 'zoom' setting


# need larger point sizes



rmss_site_buffer <- data.frame(latitude = 39.74039751943014,
                        longitude = -104.52398743305764)  %>%
  sf::st_as_sf(coords = c("longitude", "latitude"), crs = "EPSG:4326") %>%
  st_buffer(dist = 60000)

comb_map <- ggplot() +
   geom_spatraster_rgb(data = osm_tiles,
                       interpolate = TRUE) + 
    geom_sf(aes(geometry = geometry, 
                color = parameter,
                shape = parameter),
            size = 4,
          data = (epa_aqs_bbox_all %>% 
                    dplyr::select(date_local,parameter, 
                                  site_number, latitude,
                                  site_address,longitude, datum)) %>% 
            sf::st_as_sf(coords = c("longitude", "latitude"), 
                         crs = "EPSG:4326") %>% 
            unique()) + 
  scale_shape_manual(values = c(0,1,2,6,5)) +
  scale_color_viridis_d(option = 'turbo') +
    geom_sf_text(aes(geometry = geometry),
          label = "\u272a",
          size = 6,
          color = 'cyan3',
          data = (data.frame(latitude = 39.74039751943014,
                             longitude = -104.52398743305764) %>% 
                    sf::st_as_sf(coords =c("longitude", 
                                           "latitude"), 
                                 crs = "EPSG:4326"))) +
   #geom_sf(aes(geometry = geometry),
  #        alpha = 0.1,
  #        data = rmss_site_buffer) +
  geom_sf_text(aes(geometry = geometry),
          label = "\u2708",
          angle = 45,
          color = "cyan3",
          size = 5,
          data = (data.frame(latitude = 39.789861249198474,
                             longitude= -104.54965013746597)  %>%
                    sf::st_as_sf(coords = c("longitude", "latitude"),
                                 crs = "EPSG:4326"))) +
  theme_void()

save(comb_map, file = "../03_output/comb_map.rda")

# smoke map

ggplot() +
  geom_sf_text(aes(geometry = geometry),
          label = "\u272a",
          size = 5,
          color = 'cyan3',
          data = (data.frame(latitude = 39.74039751943014,
                             longitude = -104.52398743305764) %>% 
                    sf::st_as_sf(coords =c("longitude", 
                                           "latitude"), 
                                 crs = "EPSG:4326"))) +
    geom_spatraster_rgb(data = smokepoly_tiles,
                        interpolate = TRUE) +
    geom_sf(aes(geometry = geometry),
            data = smokepolys_intersects,
            alpha = 0.1) +
  theme_void()
  

```

